Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-02-25 docs/thesis/chap-cern_math_explorer.tex
work on thesis

\subsubsection{Synonym Expansion}
Even though the Unicode normalization step work for a big part of the cases presented in table \ref{unicode_characters}, there are still some groups of characters which would not be matched (Even partially), such as some types of integrals. For addressing these groups, a precomputed table was created for some general groups of characters which have some similar meaning. For each token that belongs to some of this predefined groups, a second token is created identifying the group.
For example the token <mo>{\unicodefont ∮}</mo> is expanded into <mo>{\unicodefont ∮}</mo><mo>INTEGRALS</mo>, similarly the token token <mo>{\unicodefont ∫}</mo> is expanded into <mo>{\unicodefont ∫}</mo><mo>INTEGRALS</mo> and then both will have a partial match in the INTEGRALS token. 
Unicode specification does not define a strict rule to group similar characters based on their semantics. For general operators, we used the grouping provided by Xah Lee in his website\cite{math_groups}.

@@

\subsection{Structural Features}
The structure of a mathematical equations is one of the most important features that can be extracted.

@@

\subsubsection{Specific domain structures}
Additionally, we identified patterns that are relevant and frequent in specific domains of the high energy physics. Some patterns can be as general as a derivative over time ($dx/dt$), or more specific ones like a particle decaying process ($originalParticle \rightarrow subparticle1, subparticle2, subparticle3$).

@@

\subsection{Integration with CDS}
Currently the Invenio code-base is being under a deep refactoring and rewriting. CDS currently runs in the stable branch {\codefont master} while the new developments are preferred to be implemented in the new branch {\codefont pu}. 
A demo interface over the new branch was developed to showcase the system, however to have a complete integration with CDS, a more deep work is required. 
Our system is deployed as a standalone jar which should be incorporated into a Solr instance. Also, some extra configurations should be added. Details on this can be found in appendix \ref{appendix-conf_files.}
The communication between Solr and Invenio was through the library {\codefont solrpy}.

>>>>

\subsubsection{Operator grouping}
Even though the Unicode normalization step work for a big part of the cases presented in table \ref{unicode_characters}, there are still some groups of characters which would not be matched (Even partially), such as some types of integrals. For addressing these groups, a precomputed table was created for some general groups of operators which have some similar meaning. For each token that belongs to some of this predefined groups, a second token is created identifying the group.
For example the token <mo>{\unicodefont ∮}</mo> is expanded into <mo>{\unicodefont ∮}</mo><mo>INTEGRALS</mo>, similarly the token token <mo>{\unicodefont ∫}</mo> is expanded into <mo>{\unicodefont ∫}</mo><mo>INTEGRALS</mo> and then both will have a partial match in the INTEGRALS token. 
Unicode specification does not define a strict rule to group similar characters based on their semantics. For general operators, we used the grouping provided by Xah Lee in his website\cite{math_groups}.

@@

\subsection{Structural Features}
The structure of a mathematical expression compliments the information that an be obtained over generic substructures where the naming of the variables is irrelevant.

@@

\subsubsection{Specific domain structures}
Additionally, we identified patterns that are relevant and frequent in specific domains of the high energy physics. Some patterns can be as general as a derivative over time ($dx/dt$), or more specific ones like a particle decaying process ($originalParticle \rightarrow subparticle1, subparticle2, subparticle3$) and some in the middle like the general structure of a given action: $S = \int^{t2}_{t1} \mathcal{L} dt$. The main drawback of this approach is the need to manually detect, implement and maintain long lists of patterns.

@@

\subsection{Integration with CDS}
Currently the Invenio code-base is being under a deep refactoring and rewriting. CDS currently runs in the stable branch {\codefont master} while the new developments are preferred to be implemented in the new branch {\codefont pu}. 
Our system is deployed as a standalone jar which should be incorporated into a Solr instance. Also, some extra configurations should be added. Details on this can be found in appendix \ref{appendix-conf_files}
The communication between Solr and Invenio was through the library {\codefont solrpy}. 
A demo interface over the new branch was developed to showcase the system, however to have a complete integration with CDS, a more deep work is required.

\begin{figure}
\includegraphics[height=8 cm]{figures/input_interface.png}
\label{comparison_sw_table}
\caption{Web interface of $5e^{x+y}$: Query input screen}
\end{figure}

\begin{figure}
\includegraphics[height=8 cm]{figures/results_interface.png}
\label{comparison_sw_table}
\caption{Web interface of $5e^{x+y}$: Results screen}
\end{figure}
